Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
review Table 1

@@

\paragraph{Use of fixed-point computation in the program synthesis engine}
The program synthesis engine uses fixed-point arithmetic.
Namely, we use the domain $\mathbb{R}\param{I}{F}$
for the controller's coefficients and the domain 
$\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.
Note that $I$ and $F$, as well as $I_b$ and $F_b$, 
denote the integer and fractional size, respectively, with
$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
%in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
%where $I$ and $F$ denote the integer and fractional size, respectively.
%Regarding the plant, its coefficients are this is synthesised over the 
%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
%denote the order of the polynomials representing the 
%numerator and denominator of the plant's transfer function, respectively. 
%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

\paragraph{Our synthesis problem}
The synthesis problem we are trying to solve is the following:
find a digital controller $C(z)$ %denoted by  $N_c$ and $D_c$ 
that makes the closed-loop system stable 
for all possible uncertainties 
%$\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
$\tilde G(z)$ (\ref{digital_plant_tf}).
%, where we precisely describe 
%$(\Delta N_G, \Delta D_G)$. 
% Note that, similar to the rest of the paper, we use the notation 
% $\tilda{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $C(z)$ denotes $P$ and 
$\tilde G(z)$ represents $x$.

As mentioned above, we compute the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
and those for $\tilde G(z)$ in the domain
$\mathbb{R}\langle I_b,F_b \rangle$.

@@

\begin{table}[H]
\centering
\begin{tabular}{c | l r r | r l}
Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
$G_4$ & a\_PL1\_SCH2\_IMPL1        &  16 &   4 & 2704\,s & \\
$G_4$ & a\_PL1\_SCH2\_IMPL2        &  16 &   8 & 538\,s  & \\
$G_4$ & a\_PL1\_SCH2\_IMPL3        &  16 &  12 & 12\,s   & \\
$G_4$ & a\_PL1\_SCH3\_IMPL1        &  16 &   4 & 318\,s  & \\
$G_4$ & a\_PL1\_SCH3\_IMPL2        &  16 &   8 & 967\,s  & \\
$G_4$ & a\_PL1\_SCH3\_IMPL3        &  16 &  12 & 9798\,s & \\
$G_4$ & a\_PL1\_SCH4\_IMPL1        &  16 &   4 & 6304\,s & \\
\end{tabular}

>>>>

Essentially, the synthesis problem we are trying to solve is the following:
find a digital controller denoted by  $N_c$ and $D_c$ that
makes the closed-loop system stable 
for all possible uncertainties $\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
%$(\Delta N_G, \Delta D_G)$. 
% Note that, similar to the rest of the paper, we use the notation 
% $\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
$\Delta{\vec{p}}$ represents $x$.

@@

\paragraph{Use of fixed-point computation in the program synthesis engine}
The program synthesis engine uses fixed-point arithmetic.
Thus, we compute the coefficients for $N_c$ and $D_c$ in the domains 
$\mathbb{R}^{n_C}\param{I}{F}$ and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, where 
$n_C$ and $m_C$ denote the order of the corresponding polynomials
and $I$ and $F$ denote the integer and fractional size, respectively.
Regarding the uncertainty, this is synthesised over the 
domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
denote the order of the polynomials representing the 
numerator and denominator of the plant's transfer function, respectively. 
Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

@@

\begin{table}[H]
\centering
\begin{tabular}{c | l r r | r l}
Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
$G_4$ & a\_ST1\_IMPL1        			 &  16 &   4 & 2704\,s & \\
$G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
$G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
$G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
$G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
$G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
$G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
\end{tabular}
